GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-22 paper/paper.tex
add new stuff

We have decided to take a feature matching approach of the recommendation system.
We analyze 60 gifts items and 3 common occasions and extract only 8 features.  
The features are:
\begin{tabular}{l l}
\hline\hline
Practical & Is it functional or just for decoration? \\
\hline
Meaningful & Is it has other meaning besides its function? \\
\hline
Beautiful & Is it good looking? \\
\hline
Trendy & Is it fashion? \\
\hline
Impersonal & Is it just for him/her or other people can use it? \\
\hline
Romantic & Is it present for love and sweet? \\
\hline
Geeky & Is it electrical? \\
\hline
Fun & Is it let you happy in a pure way? \\
\end{tabular}

@@

For example:
\begin{tabular}{l l}
\hline\hline
Book (Gift) & (1.0, 0.6, 0.2, 0.4, 1.0, 0.0, 0.0, 0.6) \\
\hline
Valentine’s day (Occasion) & (0.2, 1.0, 0.6, 0.2, 0.0, 1.0, 0.2, 0.2) \\
\end{tabular}

Occasion is treated differently than normal object. We sort our gift candidate from our sample pool of gifts of 20 by the mean square distance with target occasion that is specified in the UI by the users. Below the pseudocode described our first algorithm to sort gifts.

\begin{algorithm}
\caption{Mean Squared Distance sorting}
\label{mse}
\begin{algorithmic}
\STATE $X \Leftarrow x$
\end{algorithmic}
\end{algorithm}

Part 1
Pseudocode

Part 2
Pseudocode

>>>>

We have decided to take a feature matching approach of the recommendation system.
We analyze 60 gifts items and 3 common occasions and extract only 8 features.  
The features are listed in Table~\ref{features}.

\begin{table*}[ht]
\caption{Feature Vector}
\centering
\begin{tabular}{l l}
\hline
Practical & Is it functional or just for decoration? \\
\hline
Meaningful & Is it has other meaning besides its function? \\
\hline
Beautiful & Is it good looking? \\
\hline
Trendy & Is it fashion? \\
\hline
Impersonal & Is it just for him/her or other people can use it? \\
\hline
Romantic & Is it present for love and sweet? \\
\hline
Geeky & Is it electrical? \\
\hline
Fun & Is it let you happy in a pure way? \\
\end{tabular}
\label{features}
\end{table*}

@@

\noindent For instance:

\noindent \begin{tabular}{| l | l |}
\hline
Book (Gift) & (1.0, 0.6, 0.2, 0.4, 1.0, 0.0, 0.0, 0.6) \\
\hline
Birthday (Occasion) & (0.2, 1.0, 0.6, 0.2, 0.0, 1.0, 0.2, 0.2) \\
\hline
\end{tabular}

Occasion is treated differently than normal object. We sort our gift candidates from our sample pool of gifts of 20 by the mean square distance with target occasion that is specified in the UI by the users. Below the pseudocode described our first algorithm to sort gifts.

\begin{algorithm}
\caption{Mean Squared Distance sorting}
\label{mse}
\begin{algorithmic}
\STATE $HAHA \rightarrow h$
\end{algorithmic}
\end{algorithm}

However to accommodate selective considerations such as Food, Travel, Sport, etc for users who have a preference to influence the concept relatedness of the gifts candidates, we took a threshold defined for each consideration to further sort and place candidates into two buckets, a superior and inferoir for gifts that satisfied all the constraints and those not.

\begin{algorithm}
\caption{Thresholding consideration sorting}
\label{tcs}
\begin{algorithmic}
\STATE $HAHA \rightarrow h$
\end{algorithmic}
\end{algorithm}

(talk more about why and how this works etc)
